My title

### 2024-09-23 paper/paper.qmd

library(tidyverse)
```

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false
```

Talk way more about it.

@@

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false
```

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

Weaknesses and next steps should also be included.

@@

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
```

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2
```

>>>>

library(tidyverse)
library(dplyr)
library(knitr)
```

@@

# Data {#sec-data}
```{r}
#| echo: false
#| warning: false
#| message: false

bikeShare_data <- read_csv(here::here(
  "data/analysis_data/cleaned_bikeshare_data.csv"))

bikeWay_data <- read_csv(here::here("data/analysis_data/bikeway_data.csv"))
```

```{r}
#| label: fig-sample_bikeshare
#| title: Sample of Toronto's Bike Share Ridership Data
#| echo: false
#| warning: false
#| message: false

bikeShare_sample <- bikeShare_data %>% sample_n(5) %>% as_tibble()

colnames(bikeShare_sample) <- c("Trip ID", "Date")

kable(bikeShare_sample)
```

```{r}
#| label: fig-sample_bikeway
#| title: Sample of Toronto's Cycling Network Data
#| echo: false
#| warning: false
#| message: false

bikeWay_sample <- bikeWay_data %>% sample_n(5) %>% as_tibble()

colnames(bikeWay_sample) <- c("Trip ID", "Date")

kable(bikeWay_sample)
```

```{r}
#| label: fig-yearly_ridership
#| title: Yearly Bike Share Ridership
#| echo: false
#| warning: false
#| message: false

yearly_bike_share_usage <- bikeShare_data %>%
  mutate(year = year(ymd(start_date))) %>%
  group_by(year) %>%
  summarise(total_rides = n())

kable(yearly_bike_share_usage)
```

@@

@@

@@

@@

@@
